\section{Introduction}
In this lab we are going to use the techniques and theory taught in the course of optimization theory and control. To control a small helicopter model. We will be doing this by computing the optimal trajectory of the helicopter and give a corresponding input for this trajectory.

To compute this we need to derive a non-linear model for the dynamics of the system. Then linearize the model around an equilibrium. (add more context)

We will try out a few different setup to measure the performance of the optimal control computed. One where we use the optimal input directly without any feedback. Also we will try to compensate for the inaccuracy of the model by using a feedback controller. In this lab we will be using an linear-quadratic regulator to control the feedback loop.


This report is organized as follows: Section~\ref{sec:prob_descr} contains a few remarks on report writing and some random Latex advice. An example of a table can be foundin Section~\ref{sec:prob1}, along with two remarks on report writing. Section~\ref{sec:prob2} contains some advice on using plots from MATLAB. A few suggestions for making illustrations are given in Section~\ref{sec:prob3}; a matrix equation can also be found here. Section~\ref{sec:prob4} has a few comments on references and floats in Latex. The closing discussion and concluding remarks are in Sections~\ref{sec:discussion} and~\ref{sec:conclusion}, respectively. Appendix~\ref{sec:matlab} contains a MATLAB file while Appendix~\ref{sec:simulink} shows an example Simulink diagram. The Bibliography can be found at the end, on page~\pageref{sec:bibliography}.